---
title: "formative"
author: "Siyan Yin"
date: "10/5/2017"
output: html_document
---
## Upload the MITx/Harvardx dataset to R as a dataframe named D1
```{r}
D1<-read.csv("/Users/cici/formative-test-1-ysycici/HMXPC13_DI_v2_5-14-14.csv")
names(D1)
dim(D1)
summary(D1)
str(D1)
```


## What does the DI suffix that is appeneded to two of the variable names mean?
### factor


## How many people enrolled in HarvardX/CS50x recieved certification in 2012? 
### 1287
```{r}
library(dplyr)
library(tidyr)
D1 %>% filter(course_id=="HarvardX/CS50x/2012",certified==1) %>% nrow
```


## How many people registered for HarvardX/CS50x from Columbia on October 15, 2012?
### 10
```{r}
D1 %>% filter(course_id=="HarvardX/CS50x/2012",start_time_DI=="2012-10-15",final_cc_cname_DI=="Colombia") %>% nrow
```


## Create a new data frame (D2) that includes student ID and registration date for all students from a country of your choice
```{r}
a<-D1 %>% filter(final_cc_cname_DI=="United States")
D2<-a[c("userid_DI","start_time_DI","final_cc_cname_DI")]
```


## Create a new data frame (D3) in which the column names are the registration dates, with one column containing the student ids and all other cells indicating a 1 if the student registered on that date or an NA if they did not (hint: you will need to create a new variable before you change the structure of your data frame)
```{r}
b<-D1
#b<-D1[1:1000,]
b<-mutate(b,status=1)
b<-b[c("userid_DI","start_time_DI","status")]
c<-unique(b)
D3<-spread(c,"start_time_DI","status")
```


## Now make the row names of D3 the student ids on your new data frame and remove the user id column from your data frame
```{r}
D3<-select(D3,-userid_DI)
```


## Convert your data frame to a matrix (M1)
```{r}
M1<-as.matrix(D3)
```


## Create a new matrix which is the transposed version of your matrix (M2)
```{r}
M2<-t(M1)
```


## Create a third matrix (M3) that is a student by student matrix where the cells in the matrix represent if two students registered on the same day (This will take a lot of processing power, you may not be able to complete it if you have a large number of students)
```{r}
M1<-ifelse(is.na(M1)==TRUE,0,1)
M2<-t(M1)
M3<-M1%*%M2
```


## Convert the diagonal of your matrix into NAs
```{r}
diag(M3)<-NA
```

